### 2018-05-04 papers/synth/experiments.tex
experiments skeletal added

>>>>

We implemented the encodings in a tool called~\ourtool\footnote{\ashu{\url{http://add-git-hub-url}}}.
%
The tool takes a partially defined VTS as input in its custom designed
input language.
%
The tool can not only synthesize the above discussed query, but also their
combination.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
processing formulas. Since the formulas are in QBF, we cannot use~\zthree.
%
We use~\depqbf~\cite{depqbf} for solving of QBF formulas.
%
Our tool includes about ?? lines of code.

We have applied~\ourtool~on six partially defined VTS.
%
The results are presented in table~\ref{tab:qf-graph}.
%
The experiments were conducted on ... machine,
with \ashu{?}GB memory and 900s timeout.
%
The first four VTSs are synthetic and inspire from literature for typical
motifs in VTSs. 
%
The last two are the VTSs that are from .......\ashu{Describe the source of two examples}.

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
\ashu{@ankit: please discuss all the synthesis queries in the table.}
%
%
Our experiments suggest that the synthesis problems are solvable by modern
solvers and the synthesis technology may be useful for biological research.
%

### 2018-05-04 papers/synth/intro.tex
experiments skeletal added

Eukaryotic cells, including human cells, consist of multiple membrane bound compartments.
Material is transported among these compartments by the vesicle transport system (VTS) []. Briefly,
the source compartment produces a membrane bound packet of molecules called a vesicle. After
release, this vesicle specifically recognizes the correct target compartment within the cell, and fuses
with it. The molecules that form the machinery of the VTS are known. \todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other. In spite of this detailed knowledge at the level of the molecules, the structure of the VTS network, or the road-map of the eukaryotic cell, is far from complete. The current knowledge of the network is put together from a patch work of biological experiments. This information is scattered across several publications. Even after this information is collected and put together, we find that the network obtained is still not complete; new vesicles and new contents in previously known vesicles are constantly being discovered. The synthesis for the unknown pieces may be assisted by computation on the graph model of VTSs. 
% 
%In this work, we use a model described in [] to find out, given a partial
%VTS graph and details about interactions amongst its molecules, what the complete graph of the
%VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
%model.
%
%Eukaryotic cells, including human cells, consists of multiple compartments.
%
%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
%
%Almost all subsystems of the cells depend on VTSs.
%
%Therefore, understanding how VTSs functions is one of the key
%questions of cell biology.
%
In this paper, we are looking at the computational questions 
arise from the VTSs.
%
In the following, we use the model of VTSs that has been presented
in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.

% Describe VTS in detail
While VTSs transports molecules, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active or inactive in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
destination compartment.
%
Not all the pairs of molecules can participate in the fusion, the
potential fusion pairs are usually determined by biological experiments.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
A molecule that has participated in a fusion must not interfere
with fusion at different compartments or channels.
%
Therefore, the molecule must be inactive in appropriate compartments.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecules in a compartment or
channel may make the molecule active or inactive.
%
We call this regulation as {\em activity functions}.

@@

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means that the current knowledge is due to the patch work
of biological experiments~\cite{model} for identifying the compartments,
channels, molecules, and their activity and regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
For example, we may suspect that some edges may not have been
discovered in a VTS that does not satisfy the stability condition.
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, and learning activity functions.
%
We also consider variation on the properties against which we do synthesis,
namely stability, and $k$-connectedness that states
that VTS remains connected after removing any $k-1$ edges.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into a satisfiability of
quantified Boolean formulas(QBFs). 
%

We have implemented the encoding in a highly flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on two found-in-nature VTSs, namely
M1~\cite{} and S1~\cite{}.
%
We have also applied our tool on various synthetic examples to
demonstrate that our tool scale upto the graph size ??, which
is the size of typical VTSs in a eukaryotic cell.

@@

The rest of the paper is organized as follows.
%
In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
constraints on VTSs.
%
In section~\ref{sec:encoding}, we present the synthesis problems and their
encoding into QBF satisfiability.
%
In section~\ref{sec:experiments}, we present our implementation and experimental results.
%
We discuss related work in~\ref{sec:related} and conclude in section~\ref{sec:conclusion}.

>>>>

Eukaryotic cells, including human cells, consist of multiple membrane
bound compartments.
%
Material is transported among these compartments by the vesicle
transport system (VTS) [].
%
Briefly, the source compartment produces a membrane bound packet of
molecules called a vesicle.
%
After release, this vesicle specifically recognizes the correct target
compartment within the cell, and fuses with it.
%
A lot of information about the molecules that form the machinery of
the VTS has been discovered, including their regulatory interaction
with each other. 
% %
% \todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other.
%
In spite of this detailed knowledge at the level of the molecules, the
structure of the VTS network, or the road-map of the eukaryotic cell,
is far from complete.
%
The current knowledge of the network is put together from a patch work
of biological experiments and is scattered across several publications.
%
Even after this information is collected and put together, we find
that the network obtained is still not complete; new vesicles and new
contents in previously known vesicles are constantly being discovered.
%
The synthesis for the unknown pieces may be assisted by computation on
the graph model of VTSs.
%
% 
%In this work, we use a model described in [] to find out, given a partial
%VTS graph and details about interactions amongst its molecules, what the complete graph of the
%VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
%model.
%
%Eukaryotic cells, including human cells, consists of multiple compartments.
%
%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
%
%Almost all subsystems of the cells depend on VTSs.
%
%Therefore, understanding how VTSs functions is one of the key
%questions of cell biology.
%
In this paper, we are looking at the computational questions 
arise from the VTSs.

We use the model of VTSs that has been presented in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.
% Describe VTS in detail
While VTSs transports molecules, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active or inactive in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of sets of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
The molecules in both the sets must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} sets and analogously
the channel is considered to be {\em fused} with the
destination compartment.
%
Not all the pairs of set of molecule can participate in the fusion, the
potential fusion pairs are usually determined by biological experiments.
%
To ensure effective regulation, the fusing pairs must be
unique for each fused channel-compartment pair.
%
A molecule that has participated in a fusion must not interfere
with fusion at different compartments or channels.
%
Therefore, the molecule must be inactive in appropriate compartments.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecules in a compartment or
channel may make the molecule active or inactive.
%
We call this regulation as {\em activity functions}.

@@

% Partial info defence
%
As we have discussed earlier, our understanding of VTSs are partial.
%
% It largely means that the current knowledge is due to the patch work
% of biological experiments~\cite{model} for identifying the compartments,
% channels, molecules, and their activity and regulatory control.
% %
% Often the information is scattered around in several publications.
% %
% Even after with some effort we may collate all the known information about
% a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
For example, we may suspect that some edges may not have been
discovered in a VTS that does not satisfy the stability condition.
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, and learning activity functions.
%
We also consider variation on the properties against which we do
synthesis, namely stability, and $k$-connectedness that states that
VTS remains connected after removing any $k-1$ edges.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into a satisfiability of
quantified Boolean formulas(QBFs). 
%

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on two found-in-nature VTSs, namely
M1~\cite{} and S1~\cite{}.
%
We have also applied our tool on various synthetic examples to
demonstrate that our tool scale upto the graph size ??, which
is the size of typical VTSs in a eukaryotic cell.

@@

The rest of the paper is organized as follows.
%
In section~\ref{sec:example}, we present a motivating example.
%
In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
constraints on VTSs.
%
In section~\ref{sec:encoding}, we present the synthesis problems and their
encoding into QBF satisfiability.
%
In section~\ref{sec:experiments}, we present our implementation and experimental results.
%
We discuss related work in~\ref{sec:related} and conclude in section~\ref{sec:conclusion}.
